Fish do not need Visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)

### 2020-01-02 Manuscript_Draft.Rmd
Included all information needed for submission

---
title: "Fish do not need Visas: the transboundary nature of the world’s exploited marine fish species"
author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
subtitle: "DRAFT DO NOT SHARE"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
  pdf_document:
    fig_caption: yes
geometry: margin=1in
editor_options:
  chunk_output_type: inline
bibliography: ./References/FishForVisa_Ref.bib
csl: ./References/science.csl
---

@@

<!-- # Instructions for submission -->

<!-- - Journal: *Science*  -->
<!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
<!-- - There are two types of article: -->

<!-- -- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance. Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references.  -->

<!-- Policy Forums (1000 to 2000 words, 1-2 figures, and up to 15 references) presents issues related to the intersections between science and society that have policy implications. -->

<!-- In both cases Materials and Methods should be included in supplementary material -->

@@

<!-- - Reviewers: Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers. -->

<!-- # One Sentence Summary (~ 125 characters) -->

<!-- A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations. This will appear online adjacent to the title and should not repeat phrases already present there -->

<!-- - Field code: *Fisheries* -->

<!-- # **Abstract** (~125 words) -->

The precense of a species in time and space is linked to a combination of biotic and abiotic factors, but the concept of species distribution is rarely integrated into fisheries management, or policy, .

Identifying what species re transboundary is a first step to the proper management of shared stocks and achieving sustainabillity of marine ressources.

Incorporating the concept of species distribution into fisheries management, or policy, is not allways hapens as shown by the delineation of Economic Exclusive Zones (EEZs) under the United Nations Convention on the Law of the Seas (UNCLOS) in the early 80s. Shared marine ressources are inheratably complex to manage and thus, require special care. However, forty years after the formal adoption of EEZs, the question of how many shared species exist in the world based on their distribution is still unanswered. Here, we ucombine species' distributions with the nation's EEZs in order to determine the number of transboundary stocks. moreover, we identify their importance in terms of catch and revenue and discuss the

<!-- An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence. It should be a single paragraph. -->

@@

## Results and discussion (~1000 words)

@@

<!-- # **References** (up to 40 for reports and 15 for policy forum) -->

@@

<!-- ## Funding: include complete funding information;  -->
<!-- ## Authors contributions: a complete list of contributions to the paper (we encourage you to follow the CRediT model), -->
<!-- ## Competing interests: competing interests of any of the authors must be listed (all authors must also fill out the Conflict of Interest form). Where authors have no competing interests, this should also be declared. -->
<!-- ## Data and materials availability: Any restrictions on materials such as MTAs.  -->

@@

#References

>>>>

---
title: "Fish do not need Visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)"
author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, Colette Wabnitz^1,3^ and William W.L. Cheung^1^"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^Yale University, New Haven, Connecticut, USA, ^3^Stockholm Resilience Centre, Stockholm University, Stockholm, Sweden"
# subtitle: "DRAFT DO NOT SHARE"
subtitle: "Most neighbour nations share marine species (38/40 characters)"
output:
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
  pdf_document:
    fig_caption: yes
geometry: margin=1in
editor_options:
  chunk_output_type: inline
bibliography: ./References/FishForVisa_Ref.bib
csl: ./References/science.csl
---

@@

# Instructions for submission

- Journal: *Science*
<!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
<!-- - There are two types of article: -->

-- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance. Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references.

<!-- Materials and Methods should be included in supplementary material -->

@@

# Reviewers (5):
*Include Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers.*

**Note:** Please include potential reviewers you think appropiate to review the manuscript (Or confirm my suggestions)

- **Potential Reviewers (J)**  
 -- Gakushi Ishimura,  
 -- Kathleen Miller, National Center for Atmospheric Research, Boulder, Colorado, USA  
 -- Malin Pinsky, Rutgers University, New Brunswick, New Jersey, USA  
 -- Steven D. Gaines, University of California, Santa Barbara, Santa Barbara, California, USA

- **Excluded Reviewers (J)**  
-- U. Rashid Sumaila, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada  
-- Louise S.L. Teh, Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada

# One Sentence Summary (125/~125 characters)
*A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations. This will appear online adjacent to the title and should not repeat phrases already present there*

Over 50% of marine fish landings and revenue comes from species shared by neighbouring nations having direct implications to fisheries management.

# Field code (Max. 2)

- *Fisheries*

# Abstract (125/~125 words)
*An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence. It should be a single paragraph.*

Regulatory boundaries and species distributions are not always aligned, therefore marine species often cross multiple Economic Exclusive Zones (EEZs). This represents a challenge for fisheries management as the benefits from a shared resource is often maximized through collaboration. In here, we combined species distributions and the spatial delimitation of EEZs to identify the number of exploited marine fish species that are shared between neighbouring nations. We found that 64% of the world's capture and 50% or revenue comes from 633 shared species, with some countries receiving over 70% of their benefits from a few shared resources. Identifying shared species can play a critical role in the sustainability of wild fisheries suggesting a need for collaborative management strategies.

@@

<!-- ## Results and discussion (~1000 words) -->

@@

@@

<!-- ## Funding: include complete funding information;  -->
<!-- ## Authors contributions: a complete list of contributions to the paper (we encourage you to follow the CRediT model), -->
<!-- ## Competing interests: competing interests of any of the authors must be listed (all authors must also fill out the Conflict of Interest form). Where authors have no competing interests, this should also be declared. -->

## Data and materials availability
*Any restrictions on materials such as MTAs.*

Gabriel, is there any restriction with the data?

@@

# References (59/about 30)
